---
title: "Who Owns Your Research: A Survey"
author: "Jan Vitek"
date: "March 12, 2015"
output: html_document
---

```{r, echo=FALSE}
data = read.csv("Who.csv")
 colnames(data)<- c("Times", "OA_is", "OA_influence",  "Fund_OA", "Max_price", "Scaling_down", "ACM_role", "Switch",  "Copyright", "OA_comments", "Where_results", "Pub_in_journal", "Read_journal", "Pub_in_conf", "Why_journal", "Conf_as_journal", "Comment_journal", "DL_is_portal", "DL_make_easy", "DL_search", "DL_arch", "DL_comments", "Academia", "Age", "Member", "SIG", "Origin")

usa = data$Origin=="North America"
eu  = data$Origin=="Europe"
world = (!usa) & (!eu)
all = usa|eu|world
senior = data$Age == "20+ years ago"
middle = data$Age == "10+ years ago"
junior = data$Age == "<10 years ago"
rest =  (!senior) & (!middle) & (!junior)
academe = data$Academia == "academia"
industry = !academe
acm = data$Member == "yes"
notacm = !acm
pubinjournal = data$Pub_in_journal == "yes"
pubinconfer = data$Pub_in_conf == "yes"
expected = grepl("it is expected by your employer", data$Why_journal)
reg = data$Fund_OA == "through increased conference registration costs (or attendance)"
pac = data$Fund_OA == "through author processing charges"

data$Fund_OA <- as.character( data$Fund_OA )
fund_oa_comments <- data$Fund_OA[! (reg|pac) ]
data$Fund_OA[reg] <- "Registration"
data$Fund_OA[pac] <- "Author Charges"
data$Fund_OA[! (reg|pac) ] <- "Other"
data$Fund_OA <- as.factor(data$Fund_OA)

one = data$DL_is_portal == 1
two = data$DL_is_portal == 2
three = data$DL_is_portal == 3
four = data$DL_is_portal == 4
five = data$DL_is_portal == 5
na = is.na(data$DL_is_portal)

data$DL_is_portal <- as.character(data$DL_is_portal)
data$DL_is_portal[one|two] <- "No"
data$DL_is_portal[three|na] <- "Neutral"
data$DL_is_portal[four|five] <- "Yes"
data$DL_is_portal <- as.factor(data$DL_is_portal)

one = data$DL_make_easy == 1
two = data$DL_make_easy == 2
three = data$DL_make_easy == 3
four = data$DL_make_easy == 4
five = data$DL_make_easy == 5
na = is.na(data$DL_make_easy)

data$DL_make_easy <- as.character(data$DL_make_easy)
data$DL_make_easy[one|two] <- "No"
data$DL_make_easy[three|na] <- "Neutral"
data$DL_make_easy[four|five] <- "Yes"
data$DL_make_easy <- as.factor(data$DL_make_easy)

one = data$DL_search == 1
two = data$DL_search == 2
three = data$DL_search == 3
four = data$DL_search == 4
five = data$DL_search == 5
na = is.na(data$DL_search)

data$DL_search <- as.character(data$DL_search)
data$DL_search[one|two] <- "No"
data$DL_search[three|na] <- "Neutral"
data$DL_search[four|five] <- "Yes"
data$DL_search <- as.factor(data$DL_search)

one = data$DL_arch == 1
two = data$DL_arch == 2
three = data$DL_arch == 3
four = data$DL_arch == 4
five = data$DL_arch == 5
na = is.na(data$DL_arch)

data$DL_arch <- as.character(data$DL_arch)
data$DL_arch[one|two] <- "No"
data$DL_arch[three|na] <- "Neutral"
data$DL_arch[four|five] <- "Yes"
data$DL_arch <- as.factor(data$DL_arch)

total <- length(data$Times)
summary_acm <- summary(acm)
prop <- function( sum , tot) { yes=as.integer(sum[3]); as.integer(yes/tot*100) }
summary_acm_usa <- summary(acm & usa)
summary_acm_eu <- summary(acm & !usa)
summary_eu <- summary( eu )
total_eu <- as.integer(summary_eu[3])
summary_us <- summary( usa )
total_us <- as.integer(summary_us[3])
perc <- function( n, t ) {  paste0( as.integer(n/t*100),"%") }
t_orig <- table(data$Origin)
t_acad <- table(data$Academia)


#stack overflow
newpie <- pie

# Tweak the label positions - changed 1.1 to 0.7
# also commented out the lines function - so that the  
# small lines next to the labels are not plot
newlbs <- quote(if (!is.na(lab) && nzchar(lab)) {
                   #lines(c(1, 1.05) * P$x, c(1, 1.05) * P$y)
                   #text(0.7 * P$x, 0.7 * P$y, labels[i], xpd = TRUE, 
                    text(0.1 * P$x, 0.1 * P$y, labels[i], xpd = TRUE, 
                                 adj = ifelse(P$x < 0, 1, 0), cex=1.3, col="white", ...)
})

# add in the new lines of code - trial and error found the right position
body(newpie)[[22]][[4]][[7]] <- newlbs


DOA <- function( d , l ) {  cDOA( d$OA_is, d , l) }

cDOA = function( column,  d , l ) {
   d2 = data[ d , ]$OA_is
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[2] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("lightgrey","black","white"), main=l, labe=c("",ps,""), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}

pDOA <- function( d ) {
   d2 = data[ d , ]$OA_is
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[2] / total *100)
   paste0(prop,"%")
}


```

There were `r total` responses with `r prop(summary_acm, total)`% respondents being members of the ACM. Membership is higher in North America (`r prop(summary_acm_usa, total_us)`%) and lower in the rest of the world  (`r prop(summary_acm_eu, total_eu)`%). The majority of respondents are from Europe (`r perc(t_orig["Europe"],total)`) followed by the USA and Canada (`r perc(t_orig["North America"],total)`). The geographic distribution of responses is shown in the following pie chart.

```{r,echo=FALSE}
pie(summary(data$Origin),main="Origin")
```

The respondent are divided between academia (`r perc(t_acad["academia"], total)`) and industry (`r perc(t_acad["industry"],total)`). 

The relative seniority of respondents as measured by the time from their first publication is summarized in the following pie chart. 

```{r,echo=FALSE}
pie(summary(data$Age),main="Time since first publication")
```

We use the following shortcuts:  **USA** to mean responses from North America, **EU** for responses that come from Europe, **Senior** for respondent who have published their first paper more than 20 years ago, **Middle** for those who have first published ten years ago, and **Junior** for authors who have published less than 10 years ago. **ACM** will denote respondent who are members of the ACM.

**Observations:** _The survey was publicized by email to SIGPLAN and SIGPOPS members, and 
then virally through social media and personnal connections. One possible explanation for
the higher response rate from Europe is that the issues of open access are considered
more important there._


# Open Access is a Moral Imperative

On the question wether open access (OA) is a "moral imperative", `r pDOA(all)` of respondents agreed. The other responses where a "desirable features" and "not essential".  

The proportion of respondents who believe that adopting OA is a necessity depends on origin and seniority. The following table highlights the differences. Respondents outside of the **USA** were  slightly more favorable to OA (`r pDOA(!usa)`). Seniority seemed to play a big role in attitudes, with more junior respondents having stronger feelings (`r pDOA(junior|rest)`). The most striking difference is between **Senior USA Academics** and **Junior USA Academics** the former favoring OA at `r pDOA(academe & senior & usa)` and the latter at a whopping `r pDOA( academe & (junior|rest) & usa )`.

In all groups the majority views open access as a moral imperative.
<br><br><br>
<center>
```{r,echo=FALSE}

par(mfrow=c(4,3), mar=c(1, 1, 1, 0))
DOA( all , "All" )  
DOA( usa , "USA" )
DOA( !usa , "World" )
DOA( senior , "Senior" )
DOA( middle , "Mid" )
DOA( junior|rest, "Junior" )
DOA( academe & senior & usa, "Sr. US Acad." )
DOA( academe & middle & usa, "Mid. US Acad." )
DOA( academe & (junior|rest) & usa , "Jr. US Acad." )
```
</center>

**Observation:** _There seems to be little question that OA is a shared value for the community. The survey argued in favor of "Gold OA" because SIGPLAN feels that it is
important that all paper be accessible. While "Green OA" allows authors to share their
papers, it relies on authors to do so, and to make sure that OA links remain accessible. This can't be guaranteed and won't be true for older work of authors who do not have a web presence. The fact that junior authors are strongly in favor of OA is encouraging for going forward._

The question of how to fund OA divides respondents: `r perc(table(data$Fund_OA)["Author Charges"], total)` are in favor of author processing charges while 
`r perc(table(data$Fund_OA)["Registration"], total)` argue for increased conference registrations. 


```{r,echo=FALSE}
pie(summary(data$Fund_OA), main="Possible funding models")
```

The remaining suggestions for funding OA are listed next.  A number of comments suggest that a Green OA model shoud be considered. Other suggest models based on voluntary donnations similar to Wikipedia, on governmental and industry support, by increased ACM membership fees. Several comments point to arXiv as an example to follow. Lastly, some suggest cutting ACM's expenses.

**Observations:** _It is our belief that whichever model is chosen, it is crucial to prevent cases where authors would be priced out of publishing.  This can be achieved by setting the price of OA to be low enough and ensuring that exemption be available for authors unable to pay._




In the case an author processing charge was selected, how much would be a reasonable price (in USD) for a paper?  The majority of respondents, `r perc(table(data$Max_price)[1]+table(data$Max_price)[2],total)` to be precise, is willing to pay no more than $100 per paper. An additional `r perc(table(data$Max_price)[3],total)` is willing to pay $200. The following pie chart breaks the price down.

```{r,echo=FALSE}
pie(table(data$Max_price), main="Reasonable author processing charges ($)")
```

**Observation:** _A commercial publisher has offered to create a journal 
at $200 per paper. If a commercial publisher can make a profit at that price
point, it stands to reason that ACM should be able to match that price._

The issue of copyrights is fairly clear cut with `r perc(table(data$Copyright)[4],total)` in favor of  leaving copyrights with the authors.


```{r,echo=FALSE}
pie(summary(data$Copyright),main="Should authors retain copyrights to their work?")
```

The last question was wether to look for another publisher if an open access option was not available within the ACM by 2017: `r perc(table(data$Switch)[2],total)` of respondents were in favor.

```{r,echo=FALSE}


S = function(  d , l ) {
   d2 = data[ d , ]$Switch
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[2] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("lightgrey","black"), main=l, labe=c("",ps,""), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}


pie(table(data$Switch),main="Publish in OA by 2017")
```

Looking closer reveals some interesting distinctions. The majority ACM members are in favor but sentiments are stronger in Europe.

The biggest difference in opinion is between the **Senior USA ACM** members who are almost evenly split (slight majority in favor) and the **Junior** respondents who are strongly in favor of doing what it takes to get OA.

<center>
```{r,echo=FALSE}
par(mfrow=c(2,2), mar=c(1, 1, 1, 1))
S(acm, "ACM members")
S(eu, "EU")
S(senior & usa & acm, "Senior USA ACM")
S(!senior&!middle, "Junior")

```
</center>

**Observation:** _The ECOOP conference was able to switch to an open access publisher
that leaves copyright to authors within two months. Two years should be feasible, or
at least there should be a clear plan for the transition._

# Visions of ACM

The respondent provided comments about what they believed the ACM's role should be. These comments show high levels of frustration with the organization and a disconnect between how the ACM views itself and what its members want it to be.

(more detailed analyis)



# The Place of Journals

When asked where important results appear the majority of respondents (`r perc(table(data$Where_results)[3],total)`) choose conferences.

```{r,echo=FALSE}
pie(summary(data$Where_results),main="Where do important results appear?")
```

When asked wether they have published at least one paper in a journal in three years,  `r perc(table(data$Pub_in_journal)[2],total)` answer that they did not.

```{r,echo=FALSE}
pie(summary(data$Pub_in_journal),main="Have you published in a journal since 2012?")
```

There is an interesting difference between authors of different seniority levels. Junior authors are much more likely to have published a journal paper in the last three years. Why could that be?
<br><br>
<center>
```{r,echo=FALSE}

S = function(  d , l ) {
   d2 = data[ d , ]$Pub_in_journal
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[3] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("white","grey","black"), main=l, labe=c("","",ps), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}

par(mfrow=c(2  ,3), mar=c(.5, .5, .5, .1))
S(senior, "Senior")
S(middle, "Middle")
S(junior, "Junior")


```
</center>


```{r,echo=FALSE}
pie(summary(data$Read_journal),main="Have you read a journal paper since 2014?")
```

<br><br>
<center>
```{r,echo=FALSE}

S = function(  d , l ) {
   d2 = data[ d , ]$Read_journal
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[3] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("white","grey","black"), main=l, labe=c("","",ps), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}

par(mfrow=c(2  ,3), mar=c(1, 1, 1, 1))
S(senior, "Senior")
S(middle, "Middle")
S(junior, "Junior")


```
</center>


```{r,echo=FALSE}
pie(summary(data$Pub_in_conf),main="Have you published in a conference since 2013?")
```



<br><br>
<center>
```{r,echo=FALSE}

S = function(  d , l ) {
   d2 = data[ d , ]$Pub_in_conf
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[3] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("white","grey","black"), main=l, labe=c("","",ps), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}

par(mfrow=c(2  ,3), mar=c(1, 1, 1, 1))
S(senior, "Senior")
S(middle, "Middle")
S(junior, "Junior")


```
</center>

The next question tried to understand what were the factors that influenced authors to publish in journal (especially since the majority do not believe it is the place for the most important work in the field).


```{r,echo=FALSE}
long <- grepl("they allow long", data$Why_journal)
complete <- grepl("they allow one to present completed research", data$Why_journal)
reviews <- grepl("they provide better reviews", data$Why_journal)
prestige <- grepl("they are more prestigious", data$Why_journal)
expect <- grepl("it is expected by your employer", data$Why_journal)

c_long <- table(long)[2]
c_complete <- table(complete)[2]
c_reviews <- table(reviews)[2]
c_prestige <- table(prestige)[2]
c_expect <- table(expect)[2]

pie(c(c_long,c_complete,c_reviews,c_prestige,c_expect), label=c("allow long form", "allow completed research", "better reviews", "more prestigious",
                                                                 "expected by employer"), main="Why publish in journals?")
```



The next set of pie charts shows the importance of the emplpoyer's expectation. Overall, 38% of senior authors believe that employers require journal papers while only 26% of junior authors believe the same.  

If we focus on respondents from the EU these numbers increase to 47% and 33% respectively.

If we further focus on European respondents who are authors of journal papers we find that 50% of senior authors and 42% of junior authors believe they have to publish journal papers for career reasons.

<br><br>
<center>
```{r,echo=FALSE}

S = function(  d , l ) {
   d2 = expect[ d  ]
   total= sum(table(d2))
   prop = as.integer(table(d2)[2] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("white", "black","grey"), main=l, labe=c("",ps,""), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}

par(mfrow=c(3  ,3), mar=c(1, 1, 1, 1))
S(senior , "Senior")
S(middle , "Middle")
S(!senior & !middle, "Junior")

S(senior & eu, "Senior EU")
S(middle & eu, "Middle EU")
S((!senior & !middle) & eu, "Junior EU")

S(senior & eu & pubinjournal, "Senior EU Pub. in Journal")
S(middle & eu &pubinjournal, "Middle EU Pub in Journal")
S((!senior & !middle) & eu &pubinjournal, "Junior EU Pub. in Journal")
```
</center>


# State of the DL

The ACM Digital Library splits respondents approximately as many feel that it makes it 
easy to find articles.


```{r,echo=FALSE}
pie(summary(data$DL_make_easy), main="The DL makes it easy to find articles?")

```


The opinions are similarly split as to whether the search facility that is part
of the DL should be replaced by a commercial search engine.

```{r,echo=FALSE}
pie(summary(data$DL_search), main="DL’s search should be replaced by a commercial search engine?")

```

More respondents are in favor of using a system such as arXiv to archive 
the ACM's paper rather than maintaining a dedicated one.

```{r,echo=FALSE}
pie(summary(data$DL_arch), main="The DL’s archiving facility should be replaced with ArXiv?")

```


The textual comments suggest quite some frustration with the DL, it's functionality and the fact that it is behind a paywall.


# ACM's role Comments


```{r,echo=FALSE}
data$ACM_role[ data$ACM_role !=""]
```



# OA Funding Comments

```{r,echo=FALSE}
fund_oa_comments
```

# OA General Comments
```{r,echo=FALSE}
data$OA_comments[data$OA_comments != ""]
```

# DL Comments

```{r,echo=FALSE}

data$DL_comments[ data$DL_comments != ""]
```

