---
title: "Who Owns Your Research: A Survey"
author: "J. Vitek, J. Gibbons, ..."
date: "March 12, 2015"
output: html_document
---

```{r, echo=FALSE}
data = read.csv("Who.csv")
 colnames(data)<- c("Times", "OA_is", "OA_influence",  "Fund_OA", "Max_price", "Scaling_down", "ACM_role", "Switch",  "Copyright", "OA_comments", "Where_results", "Pub_in_journal", "Read_journal", "Pub_in_conf", "Why_journal", "Conf_as_journal", "Comment_journal", "DL_is_portal", "DL_make_easy", "DL_search", "DL_arch", "DL_comments", "Academia", "Age", "Member", "SIG", "Origin")

usa = data$Origin=="North America"
eu  = data$Origin=="Europe"
world = (!usa) & (!eu)
all = usa|eu|world
senior = data$Age == "20+ years ago"
middle = data$Age == "10+ years ago"
junior = data$Age == "<10 years ago"
rest =  (!senior) & (!middle) & (!junior)
academe = data$Academia == "academia"
industry = !academe
acm = data$Member == "yes"
notacm = !acm
pubinjournal = data$Pub_in_journal == "yes"
pubinconfer = data$Pub_in_conf == "yes"
expected = grepl("it is expected by your employer", data$Why_journal)
reg = data$Fund_OA == "through increased conference registration costs (or attendance)"
pac = data$Fund_OA == "through author processing charges"

data$Fund_OA <- as.character( data$Fund_OA )
fund_oa_comments <- data$Fund_OA[! (reg|pac) ]
data$Fund_OA[reg] <- "Registration"
data$Fund_OA[pac] <- "Author Charges"
data$Fund_OA[! (reg|pac) ] <- "Other"
data$Fund_OA <- as.factor(data$Fund_OA)

one = data$DL_is_portal == 1
two = data$DL_is_portal == 2
three = data$DL_is_portal == 3
four = data$DL_is_portal == 4
five = data$DL_is_portal == 5
na = is.na(data$DL_is_portal)

data$DL_is_portal <- as.character(data$DL_is_portal)
data$DL_is_portal[one|two] <- "No"
data$DL_is_portal[three|na] <- "Neutral"
data$DL_is_portal[four|five] <- "Yes"
data$DL_is_portal <- as.factor(data$DL_is_portal)

one = data$DL_make_easy == 1
two = data$DL_make_easy == 2
three = data$DL_make_easy == 3
four = data$DL_make_easy == 4
five = data$DL_make_easy == 5
na = is.na(data$DL_make_easy)

data$DL_make_easy <- as.character(data$DL_make_easy)
data$DL_make_easy[one|two] <- "No"
data$DL_make_easy[three|na] <- "Neutral"
data$DL_make_easy[four|five] <- "Yes"
data$DL_make_easy <- as.factor(data$DL_make_easy)

one = data$DL_search == 1
two = data$DL_search == 2
three = data$DL_search == 3
four = data$DL_search == 4
five = data$DL_search == 5
na = is.na(data$DL_search)

data$DL_search <- as.character(data$DL_search)
data$DL_search[one|two] <- "No"
data$DL_search[three|na] <- "Neutral"
data$DL_search[four|five] <- "Yes"
data$DL_search <- as.factor(data$DL_search)

one = data$DL_arch == 1
two = data$DL_arch == 2
three = data$DL_arch == 3
four = data$DL_arch == 4
five = data$DL_arch == 5
na = is.na(data$DL_arch)

data$DL_arch <- as.character(data$DL_arch)
data$DL_arch[one|two] <- "No"
data$DL_arch[three|na] <- "Neutral"
data$DL_arch[four|five] <- "Yes"
data$DL_arch <- as.factor(data$DL_arch)

total <- length(data$Times)
summary_acm <- summary(acm)
prop <- function( sum , tot) { yes=as.integer(sum[3]); as.integer(yes/tot*100) }
summary_acm_usa <- summary(acm & usa)
summary_acm_eu <- summary(acm & !usa)
summary_eu <- summary( eu )
total_eu <- as.integer(summary_eu[3])
summary_us <- summary( usa )
total_us <- as.integer(summary_us[3])
perc <- function( n, t ) {  paste0( as.integer(n/t*100),"%") }
t_orig <- table(data$Origin)
t_acad <- table(data$Academia)


#stack overflow
newpie <- pie

# Tweak the label positions - changed 1.1 to 0.7
# also commented out the lines function - so that the  
# small lines next to the labels are not plot
newlbs <- quote(if (!is.na(lab) && nzchar(lab)) {
                   #lines(c(1, 1.05) * P$x, c(1, 1.05) * P$y)
                   #text(0.7 * P$x, 0.7 * P$y, labels[i], xpd = TRUE, 
                    text(0.1 * P$x, 0.1 * P$y, labels[i], xpd = TRUE, 
                                 adj = ifelse(P$x < 0, 1, 0), cex=1.3, col="white", ...)
})

# add in the new lines of code - trial and error found the right position
body(newpie)[[22]][[4]][[7]] <- newlbs


DOA <- function( d , l ) {  cDOA( d$OA_is, d , l) }

cDOA = function( column,  d , l ) {
   d2 = data[ d , ]$OA_is
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[2] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("lightgrey","black","white"), main=l, labe=c("",ps,""), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}

pDOA <- function( d ) {
   d2 = data[ d , ]$OA_is
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[2] / total *100)
   paste0(prop,"%")
}


```

There were `r total` responses with `r prop(summary_acm, total)`% respondents being members of the ACM. Membership is higher in North America (`r prop(summary_acm_usa, total_us)`%) and lower in the rest of the world  (`r prop(summary_acm_eu, total_eu)`%). The majority of respondents are from Europe (`r perc(t_orig["Europe"],total)`) followed by the USA and Canada (`r perc(t_orig["North America"],total)`). The geographic distribution of responses is shown in the following pie chart.

```{r,echo=FALSE}
pie(summary(data$Origin),main="Origin")
```

The respondent are divided between academia (`r perc(t_acad["academia"], total)`) and industry (`r perc(t_acad["industry"],total)`). 

The relative seniority of respondents as measured by the time from their first publication is summarized in the following pie chart. 

```{r,echo=FALSE}
pie(summary(data$Age),main="Time since first publication")
```

We use the following shortcuts:  **USA** to mean responses from North America, **EU** for responses that come from Europe, **Senior** for respondent who have published their first paper more than 20 years ago, **Middle** for those who have first published ten years ago, and **Junior** for authors who have published less than 10 years ago. **ACM** will denote respondent who are members of the ACM.

**Observations:** _The survey was publicized by email to SIGPLAN and SIGPOPS members, and 
then virally through social media and personnal connections. One possible explanation for
the higher response rate from Europe is that the issues of open access are considered
more important there._


# Open Access is a Moral Imperative

On the question wether open access (OA) is a "moral imperative", `r pDOA(all)` of respondents agreed. The other responses where a "desirable features" and "not essential".  

The proportion of respondents who believe that adopting OA is a necessity depends on origin and seniority. The following table highlights the differences. Respondents outside of the **USA** were  slightly more favorable to OA (`r pDOA(!usa)`). Seniority seemed to play a big role in attitudes, with more junior respondents having stronger feelings (`r pDOA(junior|rest)`). The most striking difference is between **Senior USA Academics** and **Junior USA Academics** the former favoring OA at `r pDOA(academe & senior & usa)` and the latter at a whopping `r pDOA( academe & (junior|rest) & usa )`.

In all groups the majority views open access as a moral imperative.
<br><br><br>
<center>
```{r,echo=FALSE}

par(mfrow=c(4,3), mar=c(1, 1, 1, 0))
DOA( all , "All" )  
DOA( usa , "USA" )
DOA( !usa , "World" )
DOA( senior , "Senior" )
DOA( middle , "Mid" )
DOA( junior|rest, "Junior" )
DOA( academe & senior & usa, "Sr. US Acad." )
DOA( academe & middle & usa, "Mid. US Acad." )
DOA( academe & (junior|rest) & usa , "Jr. US Acad." )
```
</center>

**Observation:** _There seems to be little question that OA is a shared value for the community. The survey argued in favor of "Gold OA" because SIGPLAN feels that it is
important that all paper be accessible. While "Green OA" allows authors to share their
papers, it relies on authors to do so, and to make sure that OA links remain accessible. This can't be guaranteed and won't be true for older work of authors who do not have a web presence. The fact that junior authors are strongly in favor of OA is encouraging for going forward._

The question of how to fund OA divides respondents: `r perc(table(data$Fund_OA)["Author Charges"], total)` are in favor of author processing charges while 
`r perc(table(data$Fund_OA)["Registration"], total)` argue for increased conference registrations. 


```{r,echo=FALSE}
pie(summary(data$Fund_OA), main="Possible funding models")
```

The remaining suggestions for funding OA are listed at the end of this document.  A number of comments suggest that a Green OA model shoud be considered. Other suggest models based on voluntary donnations similar to Wikipedia, on governmental and industry support, by increased ACM membership fees. Several comments point to arXiv as an example to follow. Lastly, some suggest cutting ACM's expenses.

**Observations:** _It is our belief that whichever model is chosen, it is crucial to prevent cases where authors would be priced out of publishing.  This can be achieved by setting the price of OA to be low enough and ensuring that exemption be available for authors unable to pay._

In the case an author processing charge was selected, how much would be a reasonable price (in USD) for a paper?  `r perc(table(data$Max_price)[1]+table(data$Max_price)[2],total)` of respondents is willing to pay no more than $100 per paper. An additional `r perc(table(data$Max_price)[3],total)` is willing to pay $200. The following pie chart breaks the price down.

```{r,echo=FALSE}
pie(table(data$Max_price), main="Reasonable author processing charges ($)")
```

**Observation:** _A commercial publisher has offered to create a journal 
at $200 per paper. If a commercial publisher can make a profit at that price
point, it stands to reason that ACM should be able to match that price._

The issue of copyrights is fairly clear cut with `r perc(table(data$Copyright)[4],total)` in favor of  leaving copyrights with the authors.


```{r,echo=FALSE}
pie(summary(data$Copyright),main="Should authors retain copyrights to their work?")
```

The  next question was wether to look for another publisher if an open access option was not available within the ACM by 2017: `r perc(table(data$Switch)[2],total)` of respondents were in favor.

```{r,echo=FALSE}


S = function(  d , l ) {
   d2 = data[ d , ]$Switch
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[2] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("lightgrey","black"), main=l, labe=c("",ps,""), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}


pie(table(data$Switch),main="Publish in OA by 2017")
```

Looking closer reveals some interesting distinctions. The majority ACM members are in favor but sentiments are stronger in Europe.

The biggest difference in opinion is between the **Senior USA ACM** members who are almost evenly split (slight majority in favor) and the **Junior** respondents who are strongly in favor of doing what it takes to get OA.

<center>
```{r,echo=FALSE}
par(mfrow=c(2,2), mar=c(1, 1, 1, 1))
S(acm, "ACM members")
S(eu, "EU")
S(senior & usa & acm, "Senior USA ACM")
S(!senior&!middle, "Junior")

```
</center>

**Observation:** _The ECOOP conference was able to switch to an open access publisher
that leaves copyright to authors within two months. Two years should be feasible, or
at least there should be a clear plan for the transition._

Some of the comments on OA. All of them at the bottom of the file.

```
[8] I find the discussion of only two options (Gold and Green) a little confusing. Does a model like LIPIcs fall in the Gold option? Should there be a special notion of 'non-commercial' Gold (I don't know how to call it)? Just a thought… That being said, I think that Open Access is an absolute must, and that the way scientific publishing goes, is changing and will continue changing. Let us start with our own backyard: CS, conferences and then (different set of problems) journals, and then (again different set of problems) books                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            

[11] Open access to scientific research is a must. The nominal fee can be charged from institutions at a wholesome price and should be made available at cheap prices to independent researchers.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  

[13] In this day and age, I take it as a given that research publications should be freely available on the Internet. That ship sailed several years ago.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          

[14] Older math journals had "page fees" which were paid when authors had grants, but could be ignored otherwise.  I would be very opposed to charging authors unless there was a reasonable plan for waiving fees for those without grant support.  Otherwise only the rich could afford to publish.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              

[15] Scientists say they're contributing to the world's knowledge, but without open access, they're only contributing to only a small elite's knowledge.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           

[16] Seems like cost is always raised as an issue. Some good study/report on how much the cost is, exactly where the money goes, and improved transparency in general would be great.  I am a strong supporter of open access, given that most of the world outside of western nations are unable to access content without it.  However, I would be willing to concede author processing fees and what not if I knew where the money is going, who is getting paid. I would like this information to be easily available. Then I can decide if the causes are ones I want to support.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         

[23] First, let's get something clear: The ACM already has publication charges for conferences.  We just call them conference registration fees.  I chose "through increased conference registration costs", but if we piggybacked on the arXiv, *and* we wanted to "pay our own way", the "increased cost" would be on the order of $5 per paper.  Compared to current conference fees, $5 is a rounding error.  I'm not convinced we *would* have to pay our own way: many workshops publish their proceedings in EPTCS, which piggybacks on the arXiv and, AFAIK, doesn't pay the arXiv for that privilege.  (Aside: The statement that in Green OA, "[papers] may not be preserved in perpetuity, and [have] no centralized index" isn't really true if you put your papers on the arXiv.  Yes, the ACM's publication contract has misleading (intentionally misleading, I suspect) language that tries to make you think you can't—some nonsense about giving me the right to post a "pre-peer review" version; that right is not theirs to give or take away.  The ACM has no rights to my paper whatsoever until I sign the agreement.  If I choose to post a *post*-peer review version one minute before I sign the agreement, the ACM is powerless to stop me.)                                                                                                                                                                                                                                                                                                                                                                                                                                                                    

[25] The current mixed model (Gold OA at the choice of the authors and at a very high price) does not work. For example, the Max Planck Society is strongly supporting OA and paying for publication fees at OA journals, but does not fund the ACM OA fees because they are already paying for the DL subscription and they consider the ACM OA fees as double-charging.  We should either have Gold OA for all articles at a reasonable cost or just switch to ArXiv or LIPIcs.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               

[26] The lack of Open Access has already cost us Aaron Swartz and is one of the biggest barriers to the continued viability of academia and scholastic involvement in the 21st century. People are already dismissing the role of "ivory tower" academic organizations as "dated." It's very hard to justify charging money for access to articles when joe bloggs can write a post that "seems legit" and thoughtful content is hidden behind a paywall.  This is a moral and ethical issue about the future of our field. If you present it as such to members and ask if they would be ok with paying higher dues to enable this, I'm sure many would say yes.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                

[29] The "green" OA model is perfect, in my opinion. It allows authors to disseminate their work in a variety of ways while still allowing ACM to make their money, which overall I think they spend pretty well.  I think long-term, free repositories like arXiv are important, but need not be the focus of ACM.  I would definitely not use any publisher that prohibits publicly sharing my own papers, but ACM providing full-fledged "gold" OA is just not important to me.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             

[32] Gold OA has major biases, such as restricting the submission to authors who can afford; also, the publisher can put pressure on the reviewers to accept papers since it increases its income.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                 

[37] My work is, de facto, already (Green) Open Access (it is publicly available on my or co-author's webpage). I have no incentive to pay an overhead for the "Gold Open Access" -- which does not mean I am not interested in Open Access, I strongly believe it is essential for public research. Any conclusion drawn from the lack of interest for paid Gold options is deceptive.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            

[38] I was first tempted to mark "desirable feature" in the first question.  Then I realized that the majority of papers reports on research funded by public bodies e.g. From taxpayers money. In this light, it is unacceptable that these result are not freely accessible to the general public.  OA may even make research more honest. For example, if everybody could easily check up on scientific studies quoted in the press, then we were less prone to manipulation by journalists. Also, some authors might be ashamed that they publish a ton of crappy papers (I'm primarily thinking of medicine, but I'm sure there are lots of papers written for the sake of incrementing a publication counter).                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             

[39] The regular (big) increase of digital library subscription fees put universities in very difficult position. The current model is not sustainable and must evolve quickly. Institutions (universities) already pay (the salary of authors) for the scientific work, the redaction work, the review work, the scientific committee work, ... If they pay the reminding (through library subscription fees), the work must be put in open access AND the reminding work must be done by non-profit organization. Its is non ethical that universities offer big profits for commercial organizations.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          

[46] I'm generally happy with the policy of SIGPLAN conferences on Green open access (and they seem to meet the open access requirements in the UK where I am). However, if LIPIcs can do open access for a $15 charge, I would much prefer conferences to publish there than with the ACM.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        

[53] I don't think you can hope that SoCG will be back to ACM.  You may avoid that other conferences leave.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      

[58] ArXiv and LIPIcs are good example of how it should work                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       

[67] I think it's important to have as low a barrier of access as possible to everyone to be able to check research. If I (as a private person, not a researcher) read a story in a newspaper about some research, I want to be able to check the original source without paying. We can't educate the general public to be critical of so-called "science" and distinguish real science from pseudo-science if the general public has no access to real science.  Lacking open access by a publisher, I think it is essential that authors retain the copyright or at the very least the right to self-publish their results. But open access by a publisher is preferrable because of peer review.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             

[69] I strongly object to your explanation of OA above and on the page that led me to this survey. Apart from being incorrect with respect to the generally accepted meaning of OA, see for instance Wikipedia, it is polemic that has absolutely no place in a survey.  Why bother with all of the questions when what you really want is a single question asking if I agree with you and with YES as the only allowed choice?  Any use of the results of this survey that does not explicitly explain that the survey starts with a redefinition of the meaning of OA is bogus and inappropriate. Please do not pretend that it is a neutral attempt to gather information.  Even the title "Who owns your research?" is very misleading since ownership of the *research* is not the same as ownership of an article that describes the research, the right to publish such an article, or the right to access such a publication.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       

[71] Free access to scientific knowledge is a basic human right.  Gold open access is the most direct way to protect this right.  Using funds raised from non-open-access publications model to fund other things (even "good works" that I agree are worthy) is contrary to ACM's mission and indeed, morally questionable.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       

[72] Main funding agency in Sweden requires final version of all publications to be released under CC-BY from 2017.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                

[101] Essential for letting research have a societal impact.  We want to practioners to read our research. Therefore it must be available, without a paywall. This calls for open access.  Peerj and Usenix are teaching ACM what can be done. In line with peerj, I expect my membership costs to cover open access publication.  For peerj I pay once in my life. For ACM I am willing to pay every year, whic is a lot more. I expect to get at least what I get at peerj for that.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       

[104] Open Access is becoming a fact of life. If traditional publishers (ACM, IEEE, Wiley, Springer, Elsevier) do not adhere to it at an affordable price for authors, authors will go away to the newcomers on the market that are offering free of charge open access solutions, since the "research publication market" is changing rapidly.  In my view, all scientific research should be openly accessible at all times and to everyone. It is one of the main criteria of science to be reproducible and refutable. If research is not freely accessible, it becomes harder to reproduce it accept by the happy few.  Another important aspect is take-up of academic research by industry. By making it open access it will become easier for companies to access the published material. Otherwise, they do not have any incentive to "buy" the scientific papers.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     

[116] I feel like ACM is missing out on at least tracking proper download statistics by not being open access. People at my research lab who hit the paywall either go to CiteSeer/scholar.google or ask one of us with personal subscriptions to grab them the paper, if they can't easily find it via search (mostly for older journal papers not at ACM).                     
                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                   
[120] Open access is absolutely essential - unread research is worthless research, and we can't expect that the world as a whole will join the ACM and pay DL subscription fees just so they can _check_ if one paper per year is relevant to their problems. It exists in practice anyway, because various kinds of unofficial preprints are scattered around the Internet, but this practice undermines the importance of the DL.  Finally, the research is most often funded by the general public. The public should have a right to it. In particular, keeping knowledge away from those with fewest resources is counter to the spirit of scientific inquiry.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               

[122] While open access reduces revenue on publications, it also reduces the cost, because a component of cost is access control.  I believe we could keep publishing charges affordable.  We should also be working with funding agencies to build support of open publication venues into grant funding as a matter of course, even possibly decoupled from grants to individual researchers.  It would make a lot of sense for NSF, ERC, etc to negotiate lump-sum support of open digital libraries in lieu of publication charges on each individual grant.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    

[123] Publishing used to be a genuine community service, and it made sense for organizations like ACM to participate in it as a real community building exercise.  This is no longer true, the (traditional) publishing model is now a hindrance to the community, and organizations like ACM should get out of this business and focus on the things that their communities need today.  As an academic, my one and only goal is to have people read my work. When the best way to do this was with paper copies, it made complete sense for ACM to help me with this goal by printing and distributing paper copies. Now that digital copies are free, the traditional publishing model only gets in the way of this goal, by erecting cost, legal, and hassle barriers to getting my work read.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                

[125] There should be economies of scale through open access. As I mentioned above, in AI we have two FREE OA journals: JAIR and JMLR. They operate on a shoestring primarily through volunteer efforts.   The AAAI similarly provides open access to all conference publications at no charge to either the author or the reader.   Authors are not always in a position to pay publications charges.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          

[141] The role of academia is supposed to be to produce new knowledge and share it with the world. All researchers have an obligation to the general public. Open access is absolutely imperative, and I am embarrassed that the major publication venues I send work to do not support it.  The reason for why open access would be so expensive is not clear to me. Authors take on the role of writing, formatting, and copy-editing their own work. Reviewers work for free. Conference organizers and journal editors work for free. Digital publication is cheap, and paper publication is increasingly unnecessary. What are the true costs of distribution?  Knowledge is priceless. It should be price-less.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           

[167] Usenix makes Open Access and author-owned copyright available on all articles for free. Why can't ACM?                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        

[184] Open access is a red herring -- what we need is *fair* access. I do not see why articles have to be available free of cost to everyone. Instead, we should try to ensure that groups that lack the ability to pay -- for instance, institutions in developing countries or students -- get discounted access to ACM publications.   In some ways, the open access model that is being proposed is as unfair as the current "closed" model. Someone has to pay for open access. If this leads to publication fees and increased conference attendance fees, we will in effect be imposing an additional tax on those who lack the ability to pay. We need to think beyond a binary choice between open and closed.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           
```

# Visions of ACM

The respondent provided comments about what they believed the ACM's role should be. 

**To support and advocate for Computer Science** is clearly understood as being a role for the ACM, but agreement is harder to find on what this exactly means.

Many respondents  identify the two main activities of the ACM as: **to organize conferences** and to **make research results broadly available**.

Interestingly very few of the respondents seem aware of the Good Works.
Few respondents seemed interested in the professional outreach efforts of the ACM.

The comments show high levels of frustration with the organization and a disconnect between how the ACM views itself and what its members want it to be. Some representative 
comments are listed next, the complete list is at the bottom of this page.

```
[2] The Good Works are important.  That's not to say there isn't bloat in ACM, but there is no other organization that maintains these important activities.                           

[7] To support computer science research and to advocate for computer scientists in society at large. Part of the latter role involves providing access to the actual research.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            

[13] Roles should be: To create a centralized platform for scientific material which is freely accessible to anyone.  Unfortunately, roles seem to be: To create a centralized platform for scientific material so that it can charge people who want to access the material (of course, not paying back authors at all).                                           

[14] It ought to be a scholarly, or scientific association, whose running certainly must be economically sustainable, but not driven by commercial notions such as increasing its gross income, etc. The drive should come from serving the scientific community, and that includes offering its members services at *very* streamlined costs, keeping in mind that this community is global, diverse (also in its financial capabilities) and constantly renewed (by the influx of young researchers). Sucking in the public resources that fund most of academic research in the world should not be a priority.     

[23] To provide a safety net for risky conferences, and to update latex class files periodically. The association is pretty must an outdated model of collaboration. We have social networks that researchers can easily tap without membership to a professional organization.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             

[26] The ACM exists to organize activities and disseminate information.  Research is for the benefit of all.  An organization -- other than the researcher -- that profits from research isn't a publisher, it's a profiteer.  The ACM can take the role of a producer, i.e., someone who pays a worker for work that can then be resold, but no one should charge for the dissemination of research and/or profit from someone else's labor without remuneration.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                      

[37] The true role or purpose of an institution is what it actually does, so its primary role, from my perspective, is to take my money (or the money of the agency funding me, i.e. taxpayers' money) and set it on fire.  If the ACM truly cared about "Good Works", it would stop trying to run a substandard version of the arXiv, stop trying to run "Webinars" for people in "industry", etc., and move to a donation model (dues plus an optional top-up donation) to fund any actual "Good Works".  I don't think this will happen, partly because, considered as a charity, the ACM's administrative overhead would be laughably high.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           

[38] It is difficult to identify a single role. Certainly being one of the 2 significant publication/conference brands in the ICT sector is extremely important, as is being an advocacy group for the sector (although this is difficult if ACM wants to be an international organisation).   Note: a lot of the ACM's good works activities seem US-focused, which (as someone in Oceania/Australiasia, a region not even mentioned in your survey!) influences my view on scaling them back.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           

[43] To enable the dissemination of science from out of individual labs and into the rest of the world. It also serves as a professional body to set an example of ethical and moral behavior, a stance currently at odds with the publication mechanisms.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  

[48] That's a good question, I don't know. I have no personal experience with the 'good works' you mentioned. I have no other experience with ACM then organizing conferences (which isn't always as smooth as one would expect, and which is way too expensive to casually attend them without having a paper there).                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     

[84] It has become quite useless.  It should get drastically closer to the community.  E.g., organizing conferences with ACM is a real pain.  Before changing the financial model for conferences and journals, ACM should become more efficient and less expensive.  Credible alternative such as DROPS exist...  the cost of publishing should not be as high as it used to be.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           

[107] In theory, to serve as a general scientific organization for computer science, and manage awards, funding, conference/journal management, and archiving in a unified way across all of CS.  In practice, we get very little bang for our buck.  ACM's resistance to OA is a symptom of this.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           

[111] I don't know. The ACM does a terrible job representing the actual interests of computer science academics on the ground. I guess it's just about "professional" interests (i.e. non-academic professional). It should be part labor organization, part political party, and part library.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              

[130] They could stop being evil.  Put all publications in the public domain and put up a .torrent with the data, and they won't have to worry about hosting.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                

[136] To take a unified and strong position on all issues relevant to the scientific discipline of computer science, prioritizing scientific principles above economic and political concerns as much as possible.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           

[146] For a significant part of its current activity: "To diminish, and go into the West". When our field was small, the need for the ACM was greater. As the field grew, ACM had to grow to continue performing the same functions. At the same time computers ironically made those functions less necessary: people can self-organize and communicate, and physical journals and conferences are no longer the only way.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  

[160] I see the ACM as an umbrella organization for managing and coordinating the different subfields of CS, providing uniform overhead support for conference and journal support. This way each SIG doesn't need to figure out its own way of publishing journals, etc.  I imagine that the ACM is also seen by some as computer science's (and maybe computer programming's) professional organization, like the APA or ABA. I certainly don't see it that way, since there don't really seem to be distinguishing characteristics between the ACM candidates for elected office, so there's no way for me to vote for people who would represent _my_ views.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           

[161] It is not the role of ACM to make large profits from conferences and publishing work of others.   This has to stop and it will stop.   ACM can just decide how they 
will survive.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  

[180] I believe an open ACM is best for everyone. Legal copyright challenges are important to pursue in cases where the authors are not given their due credit. Outside of that we should push for getting our research out to as many people as possible.Our goals should be disseminate as widely as possible not to publish and make money.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               

[185] Represent CS research and education, and its societal impact.  Publishing is a just a means. In a well functioning market this can be done by industry commercially, with reasonable not too high profit margins.  As long as the publishing market is malfunctioning, ACM can publish themselves to teach the market a lesson.  Making money on publishing to fund other activities means publishing is too expensive. as a member, I disagree with this existing practice.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                     

[186] The ACM should be a professional organization for computer scientists and a publisher of Open Access computer science research. The former role should be funded by membership fees and other revenue separate from publication. Publication should aim at public dissemination of research, not at funding other activities.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                          

[189] To help organize, facilitate, and animate the scientific community, by:  - ensuring the scientific quality of publications (facilitating the review process, providing venues to publish new works and to update old ones)  - ensuring quality and smoothness of the publication process (significant proofing with writing experts, possibly assistance with presentation/layout/typography… or ensuring the process is smooth and reactive)  - assist conference organizers in providing safe and inclusive venues (code of conduct, encouraging participation from people of diverse origins, countering community-related biases…)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           

[197] Assume financial risk for conferences. Ensure a minimum of quality for venues operating under its label. Lobby congress.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             

[208] Unclear.  Computing professionals (i.e. not necessarily researchers) would benefit from a professional association, in part to be treated as an actual profession (like, e.g., physicians).  Researchers have different needs, including publication of results and organization of conferences.  I'm not sure what the ACM is trying to do, but it looks like it's neither of those.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            

[210] To freely disseminate useful results on the internet, support conference/journal administrivia, run Grace Hopper/etc, and get the fuck out of the way. Everything else is a waste of money.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            

[211] A vampire sucking the blood of the SIGs.  The primary role of the ACM *should* be to curate and archive our work for the long term.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  

[213] Organizing conferences, managing online library publishing publications to make research more accessible (e.g. ACM crossroads, ..)  But after +7 years affiliated to ACM and regularly publishing in top conferences (e.g. CHI) I realized the organization is INEFICIANT (I would say the same for IEEE)  Any progress/innovation will only happen externally (e.g. apps, websites using ACM metadata like http://confer.csail.mit.edu/) but definitely not within ACM.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           

[234] What I WANT it to be is an organization to support the research enterprise in CS. What it APPEARS to be is an industry group and publisher.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                            

[240] The role used to be serving as a point of contact among researchers. That's an outdated role: we don't need ACM to play that role any more. We all can organize our own conferences and journals and web sites, thank you.  ACM should scale back and focus on the things that we cannot do well ourselves. For example, you could do a better job of helping us to sift through all the bijillions of papers published each year to find the ones that are most interesting and useful. In addition, you could help funding entities to more easily make sense of whether researchers are having a real impact on the world outside academia. And you could apply to NSF for grants of your own to boost efforts to translate research into teaching and practice.  Think of it this way: academic research has uncovered lots of gems--ideas of great value to other scientists, to students, and to the world at large. I don't know of any organization currently focused on discovering those gems and getting them out to the people who need them most. ACM could be that organization.  In the meantime, from what I've seen so far, you have been overly focused on small ideas. You are worried about how you'll protect your market share from the rise of open publishing, how you'll compete. Think bigger. Your role is no longer to be a publisher and conference organizer. Your role is to develop a new business model as an intermediary that serves as a connection between research and impact.  If ACM isn't going to do it, then who is?

[246] Perhaps ACM could remain an umbrella for the SIGs. I also wouldn't mind it publishing CACM at a nominal price.  I would be delighted to see ACM get out of both publishing as well as hosting conferences.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           

[274] "The Association is an international scientific and educational organization dedicated to advancing the art, science, engineering, and application of information technology, serving both professional and public interests by fostering the open interchange of information and by promoting the highest professional and ethical standards."  Open interchange of information is in the very mission of the organization. Out there in the real world, open is of course different than for free, but Gold OA is a much better model to achieve the goal and mission than the current one.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        

[301] The Good Works part seems to focus an awful much on the US when it is actually funded by researchers all over the world through conference attendance and subscriptions. This looks quite dodgy.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       

[309] a) Promoting (Evidence-Based) Research in Computing and working as an intermediary between researchers and practitioners b) Providing a key index (like the library) for all literature on computing c) Setting professional (and ethical) standards for computer scientists AND RESEARCHERS (!!) d) Don't get involved in any non-computing related stuff                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         

[310] Spread high-quality research to the public for free since in my opinion scientific research results must be accessible to everyone so that everyone can validate the results and possible can help the scientific field improve at a faster pace                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       

[311] The ACM should stick to organizing conference and making our work broadly accessible (and do both much better).                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                        

[314] I was shocked to learn that ACM operates its publishing at a profit.  ACM should embrace and advocate gold open access, with the minimum possible barrier to participation.  This seems to me to be an absolute first priority in my understanding of ACM's mission.  The idea of "good works" *increasing* the APCs or subscription costs seems to me to be simply contrary to this most important of ACM's potential for good.  Membership subscriptions are, on the other hand, an entirely appropriate means of funding good works.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                

[316] To serve its members. ACM ought not to try to get copyright for itself, to make money off its members (who, please don't forget, put in almost all of the work for free - writing reviews, generating content, organizing the conferences, etc.)                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                       

[360] The role of ACM is to support and promote the field of computer science and related disciplines. For this, it needs to combine activities that make money (at present, conferences + DL) to fund those that don't (the "Good Works"). The success of the DL is what allowed ACM to become the #1 society, ahead of IEEE CS, and yet the DL is cheaper than most DL, especially when subscribing through a consortium.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                  

[361] Provide an organisational framework for conferences. Represent the CS community in an official capacity (although clearly the extent to which ACM actually does so is debatable, particularly as the nature of the community has changed). Do 'Good Works', although it may be worth considering a division of responsibility between those two things, since I can be supportive of the latter while disagreeing with the ACM's role as representative.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                               

[405] Legacy. To paraphrase Clay Shirky in "Here Comes Everybody" once an organization exists the organization itself becomes a higher priority than whatever it was originally supposed to do, in this case distribute scientific knowledge as widely as possible. Obviously the organization is currently in the way of that goal. The papers should be in the public domain so they can be distributed. Perpituity will take care of itself if you get out of the way.                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                    
```

# The Place of Journals

**Observation:** _Conferences have a natural means of raising money: they can ask for industrial sponsorship and they charge their attendees registration fees. It is thus conceivable that conferences may be self sufficient. Journals, on the other hand, don't
have a clear funding model. It is unlikely that subscriptions would be sufficient to
cover their costs. The question is thus what is their place in an OA world?_

When asked where important results appear, `r perc(table(data$Where_results)[3],total)` of respondents indicate that important results are first published in conferences.

```{r,echo=FALSE}
pie(summary(data$Where_results),main="Where do important results appear?")
```

**Observation:** _In this respect CS seems quite different from other scientific 
disciplines. The selectivity, quality of reviews, and even length of  CS conference
papers are on par with what other disciplines would call journal articles._

When asked wether they have published at least one paper in a journal in three years,  `r perc(table(data$Pub_in_journal)[2],total)` answer that they did not.

```{r,echo=FALSE}
pie(summary(data$Pub_in_journal),main="Have you published in a journal since 2012?")
```

There is an interesting difference between authors of different seniority levels. **Junior** authors are much less likely to have published a journal paper in the last three years than **Senior** or *Middle** authors. 

<br><br>
<center>
```{r,echo=FALSE}

S = function(  d , l ) {
   d2 = data[ d , ]$Pub_in_journal
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[3] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("white","grey","black"), main=l, labe=c("","",ps), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}

par(mfrow=c(2  ,3), mar=c(.5, .5, .5, .1))
S(senior, "Senior")
S(middle, "Middle")
S(junior, "Junior")


```
</center>

**Observation:** _The fact that many respondent do not publish regularly in journals is not sufficient to conclude that journals are not relevant, but it does at least suggest that they are not essential to a career in CS._

`r perc(table(data$Read_journal)[2],total)` of respondents did not read a single journal paper in 2014.


```{r,echo=FALSE}
pie(summary(data$Read_journal),main="Have you read a journal paper since 2014?")
```

It is interesting to observe that seniority does not play a big role in reading habbits.
<br><br>
<center>
```{r,echo=FALSE}

S = function(  d , l ) {
   d2 = data[ d , ]$Read_journal
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[3] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("white","grey","black"), main=l, labe=c("","",ps), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}

par(mfrow=c(2  ,3), mar=c(1, 1, 1, 1))
S(senior, "Senior")
S(middle, "Middle")
S(junior, "Junior")


```
</center>

`r perc(table(data$Pub_in_conf)[3],total)` of respondent have published
in a conference in the last two years.

```{r,echo=FALSE}
pie(summary(data$Pub_in_conf),main="Have you published in a conference since 2013?")
```


These numbers are stable accross age groups.

<br><br>
<center>
```{r,echo=FALSE}

S = function(  d , l ) {
   d2 = data[ d , ]$Pub_in_conf
   total= sum(summary(d2))
   prop = as.integer(summary(d2)[3] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("white","grey","black"), main=l, labe=c("","",ps), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}

par(mfrow=c(2  ,3), mar=c(1, 1, 1, 1))
S(senior, "Senior")
S(middle, "Middle")
S(junior, "Junior")


```
</center>

Considering that most authors do not believe that journals are where important results appear, why do they publish in journal?  The following pie chart gives the main reasons: journals are favored because they allow long form results and because they publish completed research. It is also the case that respondent felt that their employer expects them to publish in journals.


```{r,echo=FALSE}
long <- grepl("they allow long", data$Why_journal)
complete <- grepl("they allow one to present completed research", data$Why_journal)
reviews <- grepl("they provide better reviews", data$Why_journal)
prestige <- grepl("they are more prestigious", data$Why_journal)
expect <- grepl("it is expected by your employer", data$Why_journal)

c_long <- table(long)[2]
c_complete <- table(complete)[2]
c_reviews <- table(reviews)[2]
c_prestige <- table(prestige)[2]
c_expect <- table(expect)[2]

pie(c(c_long,c_complete,c_reviews,c_prestige,c_expect), label=c("allow long form", "allow completed research", "better reviews", "more prestigious",
                                                                 "expected by employer"), main="Why publish in journals?")
```



The next set of pie charts shows the importance of the empployer's expectation. Overall, 37% of senior authors believe that employers require journal papers while only 28% of junior authors believe the same.  

If we focus on respondents from the EU these numbers increase to 47% and 34% respectively.

If we further focus on European respondents who are authors of journal papers we find that 50% of senior authors and 41% of junior authors believe they have to publish journal papers for career reasons.

<br><br>
<center>
```{r,echo=FALSE}

S = function(  d , l ) {
   d2 = expect[ d  ]
   total= sum(table(d2))
   prop = as.integer(table(d2)[2] / total *100)
   ps = paste0(prop,"%")
   f = table(d2)
   newpie(f,  col=c("white", "black","grey"), main=l, labe=c("",ps,""), col.lab="white")
   text(0,1, cex=.8 , paste0("(",total,")"))
}

par(mfrow=c(3  ,3), mar=c(1, 1, 1, 1))
S(senior , "Senior")
S(middle , "Middle")
S(junior, "Junior")

S(senior & eu, "Senior EU")
S(middle & eu, "Middle EU")
S(junior & eu, "Junior EU")

S(senior & eu & pubinjournal, "Senior EU Pub. in Journal")
S(middle & eu &pubinjournal, "Middle EU Pub in Journal")
S(junior & eu &pubinjournal, "Junior EU Pub. in Journal")
```
</center>

**Observation:** _While some have claimed that their employer has been educated to 
treat journals and conferences as equally valuable contributions. This seems to be
less true in Europe. The fact that senior European authors, who know the requirements 
of tenure,  believe so strongly that journals are needed for a succsessful career
suggests that there is still a bias towards journal publications._


```{r,echo=FALSE}
caj = as.character(data$Conf_as_journal)
caj[ caj != "yes" & caj != "no"] <- "other"
data$Conf_as_journal <- as.factor(caj)
```

`r perc(table(caj)[3],total)` of the respondent are in favor of publishing some of
out conferences as special issues of journals.

```{r,echo=FALSE}
pie(summary(data$Conf_as_journal), main="Publish our best conferences as journals?")
```

**Observations:**  _SIGPLAN proposed to the ACM  to publish the proceedings of the 
PLDI conference as a special issue of the TOPLAS. The proposal includes a beefed up
reviewing model and the assurance that long version of PLDI papers can be submitted
to another journal (even TOPLAS). SIGPLAN believes that this proposal would reinvigorate journals and erase the artificial boundary between our best work and what the rest of
the scientific community thinks of as the norm._



# State of the DL

**Observations:** _Since the DL is one big cost center for the ACM, it is reasonable 
to ask if the ACM should be in the business of search and storage._

The ACM Digital Library splits respondents approximately as many feel that it makes it 
easy to find articles.


```{r,echo=FALSE}
pie(summary(data$DL_make_easy), main="The DL makes it easy to find articles?")

```


The opinions are similarly split as to whether the search facility that is part
of the DL should be replaced by a commercial search engine.

```{r,echo=FALSE}
pie(summary(data$DL_search), main="DL’s search should be replaced by a commercial search engine?")

```

More respondents are in favor of using a system such as arXiv to archive 
the ACM's paper rather than maintaining a dedicated one.

```{r,echo=FALSE}
pie(summary(data$DL_arch), main="The DL’s archiving facility should be replaced with ArXiv?")

```


The textual comments suggest quite some frustration with the DL, it's functionality and the fact that it is behind a paywall.


# ACM's role Comments


```{r,echo=FALSE}
data$ACM_role[ data$ACM_role !=""]
```



# OA Funding Comments

```{r,echo=FALSE}
fund_oa_comments
```

# OA General Comments
```{r,echo=FALSE}
data$OA_comments[data$OA_comments != ""]
```

# DL Comments

```{r,echo=FALSE}

data$DL_comments[ data$DL_comments != ""]
```

# Journal Comments

```{r,echo=FALSE}

data$Comment_journal[ data$Comment_journal != ""]
```

