---
title: "ECOOP 2015 Author Survey"
author: "J. Vitek, for the AITO Steering  Committee"
date: "March 29, 2015"
output: html_document
---

<br>


```{r, echo=FALSE}
data = read.csv("data.csv")
 colnames(data)<- c("Timestamp","Time_Submit","Like_LNCS","Switch_OA","Like_LIPIcs", "Switch_16", "Comments", "OA_helps_Academe", "Know_rules", "Ignore_rules", "OA_helps_Industry", "OA_helps_Society", "AITO", "Switch_15", "OA_important")

## Timestamp,How many times have you submitted to ECOOP?, The use of LNCS determines my submitting to ECOOP:,Would you support ECOOP switching to a proper Open Access publisher?,Would you support publishing ECOOP with Dagstuhl LIPIcs?,Would you support switching next year (2016)?,Comments,Do you think having free copies of papers available online helps other academics?, I know the rules that govern posting copies of LNCS papers on personal or institutional sites., I post copies of papers on my personal or institutional site:,Do you think having free copies of papers available online helps people in industry?,Do you think having free copies of papers available online helps society as a whole?,Are you an AITO member?,Would you support switching this year (2015)?,How important is open access to you?

# Times Submit
first <- grepl("First",data$Time_Submit)
few <- grepl("A few",data$Time_Submit)
regular <- grepl("Consider",data$Time_Submit)

data$Time_Submit<- as.character(data$Time_Submit)
data$Time_Submit[few | regular] <- "Yes"
data$Time_Submit[first] <- "No"
data$Time_Submit<- as.factor(data$Time_Submit)


# Like LNCS
Yes <- grepl("Lightly in favor",data$Like_LNCS)  | grepl("Heavily in favor",data$Like_LNCS)
DontCare <- grepl("No real difference",data$Like_LNCS)
No <- grepl("Heavily against",data$Like_LNCS) | grepl("Slightly against",data$Like_LNCS)

data$Like_LNCS<- as.character(data$Like_LNCS)
data$Like_LNCS[Yes] <- "A positive"
data$Like_LNCS[DontCare] <- "Neutral"
data$Like_LNCS[No] <- "A negative"
data$Like_LNCS<- as.factor(data$Like_LNCS)


# Like LIPIcs
Yep <-data$Like_LIPIcs == 3  | data$Like_LIPIcs == 4
Nope <-data$Like_LIPIcs == 1  | data$Like_LIPIcs == 2
data$Like_LIPIcs <- as.character(data$Like_LIPIcs)
data$Like_LIPIcs[Yep] <- "In favor"
data$Like_LIPIcs[Nope] <- "Opposed"
data$Like_LIPIcs<- as.factor(data$Like_LIPIcs)

# Helps

Yep <-data$OA_helps_Academe == 3  | data$OA_helps_Academe == 4
Nope <-data$OA_helps_Academe == 1  | data$OA_helps_Academe == 2
data$OA_helps_Academe <- as.character(data$OA_helps_Academe)
data$OA_helps_Academe[Yep] <- "Yes"
data$OA_helps_Academe[Nope] <- "No"
data$OA_helps_Academe<- as.factor(data$OA_helps_Academe)


Yep <-data$OA_helps_Industry == 3  | data$OA_helps_Industry == 4
Nope <-data$OA_helps_Industry == 1  | data$OA_helps_Industry == 2
data$OA_helps_Industry <- as.character(data$OA_helps_Industry)
data$OA_helps_Industry[Yep] <- "Yes"
data$OA_helps_Industry[Nope] <- "No"
data$OA_helps_Industry<- as.factor(data$OA_helps_Industry)


Yep <-data$OA_helps_Society == 3  | data$OA_helps_Society == 4
Nope <-data$OA_helps_Society == 1  | data$OA_helps_Society == 2
data$OA_helps_Society <- as.character(data$OA_helps_Society)
data$OA_helps_Society[Yep] <- "Yes"
data$OA_helps_Society[Nope] <- "No"
data$OA_helps_Society<- as.factor(data$OA_helps_Society)

##
total <- length(data$Time_Submit)


perc <- function( n, t ) {  paste0( as.integer(n/t*100),"%") }

```

## Population

This survey was sent to all authors of submission to the ECOOP conference in February 2015 during the reviewing period (i.e. before decisions were made).  There were <b>`r total`</b> responses.  The majority, `r perc(length(data$Time_Submit[ data$Time_Submit == "Yes"]),total)`, were authors of previous ECOOP publications.

```{r,echo=FALSE}
 pie(table(data$Time_Submit),col=c("white","black","white"),main="Have you published at ECOOP before this year?")
```


## Publisher

When asked their opinion of LNCS the majority of respondent is neutral or negative. There was a majority, 
`r perc(length(data$Like_LIPIcs[data$Like_LIPIcs=="In favor"]),total)` in favor of using LIPIcs.

<br>

```{r,echo=FALSE}

par(mfrow=c(1,2),mar=c(1, 1, 1, 0)) 
pie(table(data$Like_LNCS),col=c("white","black","lightgrey"),main="Is publishing with LNCS desirable?")
 pie(table(data$Like_LIPIcs),col=c("black","white","white"),main="Should we publish with LIPIcs?")
```

## View of Open Access

When asked about their view of open access the majority of respondent felt that it is in the best interest of Acdemia, Industry and Society at large.

```{r,echo=FALSE}

par(mfrow=c(1,3),mar=c(1, 1, 1, 0)) 
 pie(table(data$OA_helps_Academe),col=c("white","black"),main="OA helps Academe")
 pie(table(data$OA_helps_Industry),col=c("white","black"),main="OA helps Industry")
 pie(table(data$OA_helps_Society),col=c("white","black"),main="OA helps Society")
```

## Switching to OA 

When asked if they would support ECOOP moving to an open access publishing model (in the abstract), `r perc(length(data$Switch_OA[data$Switch_OA=="Yes"]), total)` of respondent answered "Yes".

A switch to LIPIcs in 2016 was supported by `r perc(length(data$Switch_OA[data$Switch_16=="Yes"]), total)` of respondents, while
a switch in 2015 was supported by `r perc(length(data$Switch_OA[data$Switch_15=="Yes"]), total)` of the authors.

<br>

```{r,echo=FALSE}
par(mfrow=c(1,3),mar=c(1, 1, 1, 0)) 
 pie(table(data$Switch_OA),col=c("lightgrey","white","black"),main="Support switching to OA")
 pie(table(data$Switch_16),col=c("lightgrey","white","black"),main="Support switching in '16")
pie(table(data$Switch_15),col=c("lightgrey","white","black"),main="Support switching in '15")
```


## Comments

The respondents were asked to provide textual comments about OA.

```{r,echo=FALSE}
data$Comments[ data$Comments != ""]
```


### Repeatability

A PDF file with questions asked in this poll is  [here](http://janvitek.org/who/ecoop/survey.pdf).

A CSV file with answers is [here](http://janvitek.org/who/ecoop/data.csv)

A PDF file with the Google Form overview of the responses is [here](http://janvitek.org/who/ecoop/results.pdf).

The R Markdown code for this document is [here](http://janvitek.org/who/ecoop/index.Rmd).



### Acknowledgments 

Shriram Krishnamurthi provided the impetus for this poll, thanks!